\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates on progress

\medskip
In fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain. Three different cases with different set-ups will follow. The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$. For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogeneous case using a mobility ratio of $10$.

>>>>

\medskip
In figure \ref{fig:HeleShawHeter_VR10}(a), there is the description of the domain. Three different cases with different set-ups will follow. The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$. For the homogeneous case there are  two different mobility ratios of $3$ and $10$ while for the heterogeneous case only the case of  mobility ratio of $10$ will be investigated.

\medskip
As can been seen so far there is %from the fig.\ref{fig:1a_homoheleshaw_3}-%\ref{fig:1c_homoheleshaw_3}
%\ref{fig:2c_homoheleshaw_10} there is 
a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements. %Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3} 
They also provide the reader with a description of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for the Hele-Shaw case of a heterogeneous formation as this is described in figure \ref{fig:HeleShawHeter_VR10}. %\ref{fig:3b_heteheleshaw_10}-\ref{fig:3c_heteheleshaw_10}.  
 Fingers will be more profound and will start develop faster when the $MR=10$ compared to the uniform front that is developing when the $MR=3$ for the same time steps. In addition the flow patter of the fingers will be sharper and more intense when different regions with different permeabilities are introduced in the formation. The importance of this set-up is to understand how the simulation works and if the result that will produced reagarding the development and pattern of the fingers, actually follow the experimental results  and how this is developed under different permeability schemes as these has already been experimentaly tested.
